\emph{Light Exposure Behavior Assessment (LEBA)}: Development of a novel instrument to capture light exposure-related behaviours

### 2021-11-11 Supplymentary.Rmd
* Table 2 is now formatted * Polygon edge not found error is solved.
* installation script is uploaded

```{r ggplot2AppB, include=F}
apatheme=ggplot2::theme_bw()+
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        text=element_text(family = "Helvetica",),
        legend.title=element_blank(),
        axis.line.x = element_line(color='black'),
        axis.line.y = element_line(color='black'),
        panel.border = element_rect(color = "black",
                                    fill = NA,
                                    size = 1))
```

@@

```{r facIdFigAppB, fig.align='center', fig.cap='Factor Identification (A) Parallel analysis (B) Scree Plot', warning=FALSE,  out.height="100%", out.width="100%"}
cowplot::plot_grid(parallel, scree.plot, labels = "AUTO",ncol=1, label_size = 8,align = "v")

>>>>

```{r ggplot2AppB, include=F}
apatheme=ggplot2::theme_bw()+
  ggplot2::theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        #text=element_text(family = "Helvetica",),
        legend.title=element_blank(),
        axis.line.x = element_line(color='black'),
        axis.line.y = element_line(color='black'),
        panel.border = element_rect(color = "black",
                                    fill = NA,
                                    size = 1))
```

@@

```{r facIdFigAppB, fig.align='center', fig.cap='Factor Identification (A) Parallel analysis (B) Scree Plot', warning=FALSE}
cowplot::plot_grid(parallel, scree.plot, labels = "AUTO",ncol=1, label_size = 8,align = "v")

### 2021-11-11 instrument.tex
* rnev introduced
loading is much faster
supplementary analysis
* Table 2 is now formatted * Polygon edge not found error is solved.
* installation script is uploaded

\begin{longtable}[]{@{}lll@{}}
\toprule
Factor names & Items & Reliability Coefficients \\
\midrule
\endhead
\textbf{F1: Wearing blue light filters} & 1-3 & .93 \\
\textbf{F2: Spending time outdoors} & 4-9 (Item 4 is reversed) & .80 \\
\textbf{F3: Using phone and smartwatch in bed} & 10-14 & .61 \\
\textbf{F4: Using light before bedtime} & 15-18 & .72 \\
\textbf{F5: Using light in the morning and during daytime} & 19-23 &
.45 \\
\bottomrule
\end{longtable}

>>>>

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.33}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.15}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.26}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.26}}@{}}
\toprule
\begin{minipage}[b]{\linewidth}\raggedright
Factor names
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Items
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Reliability Coefficients: McDonald's Omega
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Reliability Coefficients: Cronbach's alpha
\end{minipage} \\
\midrule
\endhead
\textbf{F1: Wearing blue light filters} & 1-3 & .93 & .90 \\
F2: Spending time outdoors & 4-9 (Item 4 is reversed) & .80 & .78 \\
\textbf{F3: Using phone and smartwatch in bed} & 10-14 & .61 & .62 \\
\textbf{F4: Using light before bedtime} & 15-18 & .72 & .62 \\
\textbf{F5: Using light in the morning and during daytime} & 19-23 & .45
& .41 \\
& & .73(Total scale) & \\
\bottomrule
\end{longtable}

### 2021-11-11 manuscript.Rmd
* Table 2 is now formatted * Polygon edge not found error is solved.
* installation script is uploaded

as_tibble(desc_table) -> desc_tibble 
as_kable(desc_table, format = 'pipe') -> desc_kable #save it as a knitr::kable

@@

desc_kable %>% kable_styling(desc_kable, repeat_header_text = "Participants' Demographic Characteristics")

#desc_gt %>% gt::tab_header("Participants' Demographic Characteristics")

>>>>

as_tibble(desc_table) -> desc_tibble 
as_kable_extra(desc_table, format = "latex",booktabs = T) -> desc_kable #save it as a knitr::kable

@@

desc_kable %>% kable_styling(latex_options = c("scale_down"))

### 2021-11-11 manuscript.tex
supplementary analysis
* Successfully Knitting with appendix but formating is not right
* Table 2 is now formatted * Polygon edge not found error is solved.
* installation script is uploaded

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.35}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.14}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.18}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.18}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.08}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.08}}@{}}
\toprule
\begin{minipage}[b]{\linewidth}\raggedright
\textbf{Variable}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textbf{Overall}, N = 690
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textbf{1. EFA Sample}, N = 428
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textbf{2. CFA Sample}, N = 262
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textbf{p-value}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textbf{q-value}
\end{minipage} \\
\midrule
\endhead
\textbf{Age} & 32.95 (14.57) & 32.99 (15.11) & 32.89 (13.66) & 0.5 & 0.5 \\
\textbf{Sex} & & & & 0.14 & 0.4 \\
Female & 325 (47\%) & 189 (44\%) & 136 (52\%) & & \\
Male & 351 (51\%) & 230 (54\%) & 121 (46\%) & & \\
Other & 14 (2.0\%) & 9 (2.1\%) & 5 (1.9\%) & & \\
\textbf{Gender-Variant Identity} & 49 (7.2\%) & 33 (7.8\%) & 16 (6.2\%) & 0.4 & 0.5 \\
\textbf{Native English Speaker} & 320 (46\%) & 191 (45\%) & 129 (49\%) & 0.2 & 0.5 \\
\textbf{Occupational Status} & & & & 0.040 & 0.2 \\
Work & 396 (57\%) & 235 (55\%) & 161 (61\%) & & \\
School & 174 (25\%) & 122 (29\%) & 52 (20\%) & & \\
Neither & 120 (17\%) & 71 (17\%) & 49 (19\%) & & \\
\textbf{Occupational setting} & & & & 0.3 & 0.5 \\
Home office/Home schooling & 303 (44\%) & 194 (45\%) & 109 (42\%) & & \\
Face-to-face work/Face-to-face schooling & 109 (16\%) & 68 (16\%) & 41 (16\%) & & \\
Combination of home- and face-to-face- work/schooling & 147 (21\%) & 94 (22\%) & 53 (20\%) & & \\
Neither (no work or school, or in vacation) & 131 (19\%) & 72 (17\%) & 59 (23\%) & & \\
\bottomrule
\end{longtable}

@@

@@

\end{table}
\end{appendix}

@@

Factor names

Items

Reliability Coefficients

McDonald's Omega

(N=262)

Reliability Coefficients

Cronbach's alpha

F1: Wearing blue light filters

1-3

.93

.90

F2: Spending time outdoors

4-9 (Item 4 is reversed)

.80

.78

F3: Using phone and smartwatch in bed

10-14

.61

.62

F4: Using light before bedtime

15-18

.72

.62

F5: Using light in the morning and during daytime

19-23

.45

.41

.73(Total scale)

@@

\begin{appendix}
\section{}
\hypertarget{supplimentary-analysis}{%
\subsection{Supplimentary Analysis}\label{supplimentary-analysis}}

{\centering \includegraphics[width=1\linewidth,height=1\textheight]{manuscript_files/figure-latex/facIdFigAppB-1}

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 0\tabcolsep) * \real{1.00}}@{}}
\toprule
\begin{minipage}[b]{\linewidth}\raggedright
\textbf{Five Factor Solution{[}Unmerged Responses{]} (24 Items)}
\end{minipage} \\
\midrule
\endhead
\textbf{F1} \\
I use light therapy applying a blue light box. \\
I use light therapy applying a light visor. \\
I use light therapy applying a white light box. \\
I use light therapy applying another form of light device. \\
I use an alarm with a dawn simulation light. \\
\textbf{F2} \\
I spend more than 3 hours per day (in total) outside. \\
I spend between 1 and 3 hours per day (in total) outside. \\
I spend as much time outside as possible. \\
I spend 30 minutes or less per day (in total) outside. \\
I go for a walk or exercise outside within 2 hours after waking up. \\
I spend between 30 minutes and 1 hour per day (in total) outside. \\
\textbf{F3} \\
I look at my mobile phone screen immediately after waking up. \\
I use my mobile phone within 1 hour before attempting to fall asleep. \\
I check my phone when I wake up at night. \\
\textbf{F4} \\
I use a blue-filter app on my computer screen within 1 hour before
attempting to fall asleep. \\
I seek out knowledge on how to improve my light exposure. \\
I dim my computer screen within 1 hour before attempting to fall
asleep. \\
I discuss the effects of light on my body with other people. \\
I modify my light environment to match my current needs. \\
I dim my room light within 1 hour before attempting to fall asleep. \\
I use as little light as possible when I get up during the night. \\
\textbf{F5} \\
I wear blue-filtering, orange-tinted, and/or red-tinted glasses indoors
during the day. \\
I wear blue-filtering, orange-tinted, and/or red-tinted glasses outdoors
during the day. \\
I wear blue-filtering, orange-tinted, and/or red-tinted glasses within 1
hour before attempting to fall asleep. \\
\bottomrule
\end{longtable}
\end{appendix}

>>>>

\begin{table}

\caption{\label{tab:prepareDescTable}Dempgraphics}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{llllll}
\toprule
Variable & Overall, N = 690 & 1. EFA Sample, N = 428 & 2. CFA Sample, N = 262 & p-value & q-value\\
\midrule
Age & 32.95 (14.57) & 32.99 (15.11) & 32.89 (13.66) & 0.5 & 0.5\\
Sex &  &  &  & 0.14 & 0.4\\
\hspace{1em}Female & 325 (47\%) & 189 (44\%) & 136 (52\%) &  & \\
\hspace{1em}Male & 351 (51\%) & 230 (54\%) & 121 (46\%) &  & \\
\hspace{1em}Other & 14 (2.0\%) & 9 (2.1\%) & 5 (1.9\%) &  & \\
\addlinespace
Gender-Variant Identity & 49 (7.2\%) & 33 (7.8\%) & 16 (6.2\%) & 0.4 & 0.5\\
Native English Speaker & 320 (46\%) & 191 (45\%) & 129 (49\%) & 0.2 & 0.5\\
Occupational Status &  &  &  & 0.040 & 0.2\\
\hspace{1em}Work & 396 (57\%) & 235 (55\%) & 161 (61\%) &  & \\
\hspace{1em}School & 174 (25\%) & 122 (29\%) & 52 (20\%) &  & \\
\addlinespace
\hspace{1em}Neither & 120 (17\%) & 71 (17\%) & 49 (19\%) &  & \\
Occupational setting &  &  &  & 0.3 & 0.5\\
\hspace{1em}Home office/Home schooling & 303 (44\%) & 194 (45\%) & 109 (42\%) &  & \\
\hspace{1em}Face-to-face work/Face-to-face schooling & 109 (16\%) & 68 (16\%) & 41 (16\%) &  & \\
\hspace{1em}Combination of home- and face-to-face- work/schooling & 147 (21\%) & 94 (22\%) & 53 (20\%) &  & \\
\addlinespace
\hspace{1em}Neither (no work or school, or in vacation) & 131 (19\%) & 72 (17\%) & 59 (23\%) &  & \\
\bottomrule
\multicolumn{6}{l}{\rule{0pt}{1em}\textsuperscript{1} Mean (SD); n (\%)}\\
\multicolumn{6}{l}{\rule{0pt}{1em}\textsuperscript{2} Wilcoxon rank sum test; Pearson's Chi-squared test}\\
\multicolumn{6}{l}{\rule{0pt}{1em}\textsuperscript{3} False discovery rate correction for multiple testing}\\
\end{tabular}}
\end{table}

@@

\leavevmode\vadjust pre{\hypertarget{ref-R-extrafont}{}}%
Winston Chang. (2014). \emph{Extrafont: Tools for using fonts}. Retrieved from \url{https://CRAN.R-project.org/package=extrafont}

@@

\hypertarget{factor-analysis-with-unmerged-response-option}{%
\section{Factor Analysis with Unmerged Response
Option}\label{factor-analysis-with-unmerged-response-option}}

{\centering \includegraphics{manuscript_files/figure-latex/facIdFigAppB-1}

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 0\tabcolsep) * \real{1.00}}@{}}
\toprule
\begin{minipage}[b]{\linewidth}\raggedright
\textbf{Five Factor Solution{[}Unmerged Responses{]} (24 Items)}
\end{minipage} \\
\midrule
\endhead
\textbf{F1} \\
I use light therapy applying a blue light box. \\
I use light therapy applying a light visor. \\
I use light therapy applying a white light box. \\
I use light therapy applying another form of light device. \\
I use an alarm with a dawn simulation light. \\
\textbf{F2} \\
I spend more than 3 hours per day (in total) outside. \\
I spend between 1 and 3 hours per day (in total) outside. \\
I spend as much time outside as possible. \\
I spend 30 minutes or less per day (in total) outside. \\
I go for a walk or exercise outside within 2 hours after waking up. \\
I spend between 30 minutes and 1 hour per day (in total) outside. \\
\textbf{F3} \\
I look at my mobile phone screen immediately after waking up. \\
I use my mobile phone within 1 hour before attempting to fall asleep. \\
I check my phone when I wake up at night. \\
\textbf{F4} \\
I use a blue-filter app on my computer screen within 1 hour before
attempting to fall asleep. \\
I seek out knowledge on how to improve my light exposure. \\
I dim my computer screen within 1 hour before attempting to fall
asleep. \\
I discuss the effects of light on my body with other people. \\
I modify my light environment to match my current needs. \\
I dim my room light within 1 hour before attempting to fall asleep. \\
I use as little light as possible when I get up during the night. \\
\textbf{F5} \\
I wear blue-filtering, orange-tinted, and/or red-tinted glasses indoors
during the day. \\
I wear blue-filtering, orange-tinted, and/or red-tinted glasses outdoors
during the day. \\
I wear blue-filtering, orange-tinted, and/or red-tinted glasses within 1
hour before attempting to fall asleep. \\
\bottomrule
\end{longtable}

{\centering \includegraphics{manuscript_files/figure-latex/EFAResidualsAppB-1}

\caption{ Histogram of residulas:  five-factor solution}\label{fig:EFAResidualsAppB}
\end{figure}
\end{appendix}

@@

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.33}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.15}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.26}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.26}}@{}}
\toprule
\begin{minipage}[b]{\linewidth}\raggedright
Factor names
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Items
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Reliability Coefficients: McDonald's Omega
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Reliability Coefficients: Cronbach's alpha
\end{minipage} \\
\midrule
\endhead
\textbf{F1: Wearing blue light filters} & 1-3 & .93 & .90 \\
F2: Spending time outdoors & 4-9 (Item 4 is reversed) & .80 & .78 \\
\textbf{F3: Using phone and smartwatch in bed} & 10-14 & .61 & .62 \\
\textbf{F4: Using light before bedtime} & 15-18 & .72 & .62 \\
\textbf{F5: Using light in the morning and during daytime} & 19-23 & .45
& .41 \\
& & .73(Total scale) & \\
\bottomrule
\end{longtable}

@@
